Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-09-08 1_introduction/introduction.tex
no message

Process mining is a relatively young and developing research area with the roots in computational intelligence, data mining; and process modeling and analysis \cite{van2012process}. Main idea in this research area is to discover, monitor and improve processes by extracting information from event logs. Traditional process mining approaches work on a single organization; however, with the increase of cloud computing and shared infrastructures, event logs of multiple organizations are currently available for analysis where cross-organizational process mining stands out. In cross-organizational process mining area, recent studies focus on commonality and collaboration between organizations. Studies focus on how similar the process models and behaviors of organizations under cross comparison \cite{buijs2012towards} and challenges based on partitioning of tasks and process models between organizations \cite{van2011intra}. This study is based on the environment where processes are executed on several organizations and cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used.

>>>>

Process mining is a relatively young and developing research area with the roots in computational intelligence, data mining; and process modeling and analysis \cite{van2012process}. Main idea in this research area is to discover, monitor and improve processes by extracting information from event logs. Traditional process mining approaches work on a single organization; however, with the increase of cloud computing and shared infrastructures, event logs of multiple organizations are currently available for analysis where cross-organizational process mining stands out. In cross-organizational process mining area, recent studies focus on commonality and collaboration between organizations, especially on how similar the process models and behaviors of organizations under cross comparison \cite{buijs2012towards} and challenges based on partitioning of tasks and process models between organizations \cite{van2011intra}. This study is based on the environment where processes are executed on several organizations and cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used.

### 2015-09-08 2_relatedwork/relatedwork.tex
no message

In this section, studies related to the work presented in this thesis are summarized. Firstly, studies in the process mining area are explained and then studies from cross-organizational process mining, which is the main topic of this research, is introduced. Following these, studies related to similarity in process mining is mentioned. Finally, performance and conformance analysis approaches in process mining area are presented.

 Within the process mining framework, there are various different process mining algorithms proposed which have the same aim of discovering underlying processes. Considering the underlying approaches undertaken, algorithms can be grouped as $\alpha$-algorithms \cite{van2004workflow,de2004process}, inductive approaches \cite{herbst1998integrating,herbst2000dealing}, hierarchical clustering \cite{greco2005mining}, genetic approaches \cite{van2005genetic,esgin2010hybrid}, and heuristic approaches \cite{esgin2009hybrid}. Considering the scope of this study; process discovery operations are undertaken with inductive methods which is a robust, repeatable and mature set of approaches.

>>>>

In this section, studies related to the work presented in this research are summarized. Firstly, studies in the process mining area are explained and then studies from cross-organizational process mining, which is the main topic of this research, is introduced. Following these, studies related to similarity in process mining are presented.

Within the process mining framework, there are various different process mining algorithms proposed which have the same aim of discovering underlying processes. Considering the underlying approaches, algorithms can be grouped as $\alpha$-algorithms \cite{van2004workflow,de2004process}, inductive approaches \cite{herbst1998integrating,herbst2000dealing}, hierarchical clustering \cite{greco2005mining}, genetic approaches \cite{van2005genetic,esgin2010hybrid}, and heuristic approaches \cite{esgin2009hybrid}. Considering the scope of this study; process discovery operations are undertaken with inductive methods which is a robust, repeatable and mature set of approaches.

Cross-organizational mining is based on cross-correlation of workflows and the realized activities in different organization to compare in an objective approach. In the study of Bujis et al. \cite{buijs2012towards}, process models and behaviors of organizations are cross-compared with the idea of supporting and representing. In the studies of van der Aalst \cite{van2011business,van2011intra}, configurable process models are proposed with the ideas of \textit{exploiting commonality} and \textit{collaboration} for the organizations sharing the same infrastructure and doing the similar work. In this study, usage of cross-organizational process mining is based on \textit{exploiting commonality} where organizations can learn from each other.

Similarity in process mining have various approaches which focus on metrics \cite{dijkman2011similarity}, analytical comparison \cite{buijs2014comparing}, delta analysis \cite{esgin2011delta,esgin2013sequence} and mismatch patterns \cite{dijkman2007mismatch}. In this research, combination of metric and mismatch pattern approaches are used to identify variations between process models of different organizations that execute the same tasks.

### 2015-09-08 3_background/background.tex
no message

In this section background information is presented for the relevant topics to this thesis study. Process discovery approaches and then mismatch patterns in process models are presented. All topics in this chapter are limited to the scope of this thesis study with the aim of constructing a necessary background.

In process mining field, one of the most challenging tasks is to construct a process model based on the behavior in the event logs, namely process discovery. Many process discovery algorithms are proposed to address different challenges in process discovery and using different notations. However, in this study focus of the study is learning from the cross-organizational process mining rather than addressing all process discovery challenges. With this reasoning, Inductive Process Mining \cite{leemans2013discovering} is selected as appropriate since it is simple, highly applicable and configurable. In the literature, its derivatives which handles infrequent behaviors \cite{leemans2014discoveringinfrequent}; incomplete logs \cite{leemans2014discoveringincomplete}; and model optimization \cite{weidlich2012profiles} are also available. \textit{Inductive Miner Infrequent (IMi)} \cite{leemans2014discoveringinfrequent} extension is used in this study which is capable of filtering the infrequent behavior and results with lower fitness, higher precision and equal generalization.

In cross-organizational process mining environment, there is a need to align processes of different organizations and in this scope both the organizations and their processes are similar but have significant differences. In order to align these processes and organizations, there is a need for spotting differences between process models. In the study of Dijkman \cite{dijkman2007mismatch}, a collection of patterns to describe frequent mismatches between the similar process models are presented.Within the scope of this study, the related mismatch patterns are defined in study \cite{dijkman2007mismatch} as follows:
\begin{description}
  \item[Skipped Activity] An activity exists in one process but no equivalent activity is found in the other process.
  \item[Refined Activity] An activity exists in one process but, as an equivalent, a collection of activities are existing in the other process to achieve the same task.
  \item[Activities at Different Moments in Processes] Set of activities are undertaken with different orders in different processes.
  \item[Different Conditions for Occurrence] Set of dependencies are same for two processes; however, occurrence condition is different.
  \item[Different Dependencies] Dependency set of activities differ in different organizations.
  \item[Additional Dependencies] This pattern is a special case of different dependencies where one set of activities includes the other and results with additional dependencies.
\end{description}

>>>>

In this section process discovery methods and mismatch patterns are presented within the  the scope of this resarch thesis and the aim of constructing a necessary background.

In process mining field, various process discovery algorithms are proposed to address different challenges in process discovery and using different notations. However, in this study focus of the study is learning from the cross-organizational process mining rather than addressing all process discovery challenges. With this reasoning, Inductive Process Mining \cite{leemans2013discovering} is selected as appropriate since it is simple, highly applicable and configurable. In the literature, its derivatives which handles infrequent behaviors \cite{leemans2014discoveringinfrequent}; incomplete logs \cite{leemans2014discoveringincomplete}; and model optimization \cite{weidlich2012profiles} are also available. \textit{Inductive Miner Infrequent (IMi)} \cite{leemans2014discoveringinfrequent} extension is used in this study which is capable of filtering the infrequent behavior and results with lower fitness, higher precision and equal generalization.

In cross-organizational process mining environment, there is a need to align processes of different organizations and in this scope both the organizations and their processes are similar but have significant differences. In order to align these processes and organizations, there is a need for spotting differences between process models. In the study of Dijkman \cite{dijkman2007mismatch}, a collection of patterns to describe frequent mismatches between the similar process models are presented. Within the scope of this study, the related mismatch patterns are defined in study \cite{dijkman2007mismatch} as follows:
\begin{description}
  \item[Skipped Activity] An activity exists in one process but no equivalent activity is found in the other process.
  \item[Refined Activity] An activity exists in one process but, as an equivalent, a collection of activities are existing in the other process to achieve the same task.
  \item[Activities at Different Moments in Processes] Set of activities are undertaken with different orders in different processes.
  \item[Different Conditions for Occurrence] Set of dependencies are same for two processes; however, occurrence condition is different.
  \item[Different Dependencies] Dependency set of activities differ in different organizations.
  \item[Additional Dependencies] This pattern is a special case of different dependencies where one set of activities includes the other and results with additional dependencies.
\end{description}

### 2015-09-08 4_methodology/methodology.tex
no message

\section{Methodology}
\label{sec:methodology}
In this section, the methodology proposed in this study is presented. Firstly, approach overview is described from a high-level perspective. Then, each stage in the methodology is presented together with their importance in the study, mathematical representations and definitions; and black-box diagrams. In the last section of this chapter, implementation details of this methodology in ProM framework is explained in detail with a software architecture overview.

\subsection{Approach Overview}
\label{subsec:approach-overview}
The approach proposed in this study consists of four main stages visualized in Figure~\ref{fig:approach-overview}. Firstly, in \textit{Process Model Mining}, process models are extracted from event logs for each organization with a user specified noise threshold. Secondly, in \textit{Performance Indicator Analysis}, event logs are replayed on process models and performance indicators are calculated for each organization then using these indicators, organizations are clustered based on how well they are operating. Thirdly, in \textit{Mismatch Pattern Analysis}, differences between process models of organizations are extracted with well-established mismatch patterns. Finally, in \textit{Recommendation Generation}, using the performance indicator clusterings and differences between process models, a set of recommendations for each organization is generated. In the following sections, each stage will be explained in detail with their mathematical backgrounds.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/approach-overview}
  \caption{Overview of Methodology}
  \label{fig:approach-overview}
\end{figure}

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. In order to achieve this aim, implementation of \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. Considering the scope of this study, instead of computational details of \textit{Inductive Miner Infrequent (IMi)}; black-box representation is used to explain its usage in the methodology. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to method in addition to event logs. As a result, workflow net is produced which is a sound and properly completed Petri net without deadlocks. Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

@@

\subsubsection{Replay and Performance Indicator Calculation}
\label{subsubsec:replay-and-performance-summary}
Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels. Alignment is based on \textit{moves in the model and log} and in order to have a successful replay where optimal alignment should be achieved. As proposed in \cite{adriansyah2011conformance,adriansyah2011towards}, $A^{*}$ algorithm which is a path-finding algorithm based on graphs is used to find optimal alignment of event logs on the process models. With the generated and user-specified inputs, replay and performance indicator calculation in the methodology can be visualized in Figure~\ref{fig:replay-and-performance-indicator-calculation}. For each organization, the steps in the diagram are followed with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/replay-and-performance-indicator-calculation}
  \caption{Replay and Performance Indicator Calculation Stage as Black-box}
  \label{fig:replay-and-performance-indicator-calculation}
\end{figure}

\subsubsection{Performance Indicator Clustering}
\label{subsubsec:performance-indicator-clustering}

Clustering is based on the idea of collecting the set of observations into clusters so that observations within the same cluster are similar whereas the observations from different clusters are dissimilar. In this thesis study, clustering is used to gather organizations based on their performance indicator data. In this study, a generic approach based on centroid-based clustering is exploited. For the fixed number of \textit{k} clusters, the approach is well-known as \textit{k-means clustering}. Considering the popularity of this approach and its extensions, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations. For each organization, \textit{Performance Summary} data is used as the data source in clustering. Since number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations. For each clustering with different number of clusters, SSE values are plotted and user is made to select the appropriate cluster size. For the selected cluster size, clustering related information is used to generate recommendations in the further steps. This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
  \caption{Performance Indicator Clustering Stage as Black-box }
  \label{fig:performance-indicator-clustering-blackbox}
\end{figure}

\subsection{Mismatch Pattern Analysis}
\label{subsec:mismatch-pattern-analysis}
In order to learn from other organizations, it is necessary to spot the differences between process models of different organizations. In this phase of methodology, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}. In the process mining stage, process models are mined to create Workflow nets; however, mismatch pattern definitions are closer to business environment and it is more suitable spot patterns in BPMN notation. Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied. After spotting differences, mismatch patterns for activities and control flows are revealed for the organizations.

Business Process Modeling Notation (BPMN) is one of the widely accepted modeling language in the industry and its a standardized notation by the Object Management Group (OMG) since 2004. In this stage, BPMN formulation is used since mismatch patterns have roots in real-life business environment \cite{dijkman2007mismatch}.

For each organization, mined process models are converted to BPMN models and mismatch patterns analysis is undertaken on them, in order to locate differences between two process models or cluster of process models. In addition, since performance indicators are calculated based on a starting and ending points in the process model, same approach is applied to locate mismatch patterns. In other words, differences of process models are located through a starting activity to an ending activity. When the complete set of mismatches between process models are required, this approach is used with starting and ending points as source and sink activities. For each organization, mismatch patterns are gathered and stored for the further analysis as visualized in Figure~\ref{fig:mismatch-pattern-analysis-blackbox}.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/mismatch-pattern-analysis-blackbox}
  \caption{Mismatch Pattern Analysis Stage as Black-box}
  \label{fig:mismatch-pattern-analysis-blackbox}
\end{figure}

@@

This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}. In addition, a performance difference threshold is gathered from the user to specify how much difference between clusters is necessary to check for mismatch patterns and generate recommendations. This stage generates recommendation data for each organization which contains a set of mismatch patterns.
\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{4_methodology/recommendation-generation-blackbox}
  \caption{Recommendation Generation Stage as Black-box}
  \label{fig:recommendation-generation-blackox}
\end{figure}

\subsection{Implementation in ProM Framework}
\label{subsec:implementation}
Methodology of this thesis study is implemented in ProM \cite{verbeek2010prom}, which is an extensible framework that supports a wide variety of process mining techniques in form of plugins. ProM is an open source framework for process mining algorithms which provides a platform to users and developers. Aim of this framework is to create a standard process mining platform that is accepted in industry and academia with an active community. Approach of this thesis study is implemented with its each stage as a standalone plugin that enables extensions for further studies. Developed set of plugins are packaged with the name of \textit{CrossOrgProcMin}\footnote{\url{http://www.promtools.org/prom6/packages/CrossOrgProcMin}} and published open-source\footnote{\url{http://github.com/onuryilmaz/cross-org-proc-min}} being available in the latest version of ProM release.

Approach of this study is divided into stand-alone stages where inputs and outputs between them are defined strictly. With the help of this understanding, each stage is developed as a stand-alone plug-in in ProM framework which can be called separately. For this aim, five plug-ins are developed which are visualized in Figure~\ref{fig:architecture} to provide a high-level perspective. In addition, a set of utilities are developed to visualize and persistence of data in ProM environment. 
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/architecture}
  \caption{Software Architecture for  Cross-Organizational Process Miner}
  \label{fig:architecture}
\end{figure}

>>>>

\section{Methodology}
\label{sec:methodology}
In this section, the methodology proposed in this study is presented. Firstly, approach overview is described from a high-level perspective. Then, each stage in the methodology is presented together with their importance in the study, mathematical representations and definitions; and black-box diagrams. Finally, implementation details of this methodology in ProM framework is explained in detail with a software architecture overview.

\subsection{Approach Overview}
\label{subsec:approach-overview}
The approach proposed in this study consists of four main stages visualized in Figure~\ref{fig:approach-overview}. Firstly, in \textit{Process Model Mining}, process models are extracted from event logs for each organization with a user specified noise threshold. Secondly, in \textit{Performance Indicator Analysis}, event logs are replayed on process models and performance indicators are calculated for each organization then using these indicators, organizations are clustered based on how well they are operating. Thirdly, in \textit{Mismatch Pattern Analysis}, differences between process models of organizations are extracted with well-established mismatch patterns. Finally, in \textit{Recommendation Generation}, using the performance indicator clusterings and differences between process models, a set of recommendations for each organization is generated.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/approach-overview}
  \caption{Overview of Methodology}
  \label{fig:approach-overview}
\end{figure}

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. In order to achieve this aim, implementation of \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to method in addition to event logs. Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

@@

\subsubsection{Replay and Performance Indicator Calculation}
\label{subsubsec:replay-and-performance-summary}
Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels. For each organization, the steps alignment and creating transitions are undertaken with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.

\subsubsection{Performance Indicator Clustering}
\label{subsubsec:performance-indicator-clustering}
Clustering is based on the idea of collecting the set of observations into clusters so that observations within the same cluster are similar whereas the observations from different clusters are dissimilar. In this study, clustering is used to gather organizations based on their performance indicator data. In this research, random initialization based \textit{k-means++} approach from the study of Arthur and Vassilvitskii \cite{arthur2007} is used to cluster organizations. Since number of clusters are not known priori, k-means clustering is applied starting \textit{k} from 1 to the number of organizations. For each clustering with different number of clusters, SSE values are plotted and user is made to select the appropriate cluster size. For the selected cluster size, clustering related information is used to generate recommendations in the further steps. This stage of methodology can be visualized as an input-output system in Figure~\ref{fig:performance-indicator-clustering-blackbox}. 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/performance-indicator-clustering-blackbox}
  \caption{Performance Indicator Clustering Stage as Black-box }
  \label{fig:performance-indicator-clustering-blackbox}
\end{figure}

\subsection{Mismatch Pattern Analysis}
\label{subsec:mismatch-pattern-analysis}
In order to learn from other organizations, it is necessary to spot the differences between process models of different organizations. In this phase of methodology, differences between process models will be revealed by the mismatch patterns which are defined by Dijkman \cite{dijkman2007mismatch}. In the process mining stage, process models are mined to create Workflow nets; however, mismatch pattern definitions are closer to business environment and it is more suitable spot patterns in BPMN notation. Thus, mined process models are converted to BPMN models and then mismatch pattern analysis is applied in order to locate differences between two process models or cluster of process models. In addition, since performance indicators are calculated based on a starting and ending points in the process model, same approach is applied to locate mismatch patterns. In other words, differences of process models are located through a starting activity to an ending activity. For each organization, mismatch patterns are gathered and stored for the further analysis as visualized in Figure~\ref{fig:mismatch-pattern-analysis-blackbox}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{4_methodology/mismatch-pattern-analysis-blackbox}
  \caption{Mismatch Pattern Analysis Stage as Black-box}
  \label{fig:mismatch-pattern-analysis-blackbox}
\end{figure}

@@

This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}. In addition, a performance difference threshold is gathered from the user to specify how much difference between clusters is necessary to check for mismatch patterns and generate recommendations. This stage generates recommendation data for each organization which contains a set of mismatch patterns.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/recommendation-generation-blackbox}
  \caption{Recommendation Generation Stage as Black-box}
  \label{fig:recommendation-generation-blackox}
\end{figure}

\subsection{Implementation in ProM Framework}
\label{subsec:implementation}
Methodology of this study is implemented in ProM \cite{verbeek2010prom}, which is an extensible framework that supports a wide variety of process mining techniques in form of plugins. Approach of this study is implemented with its each stage as a standalone plugin that enables extensions for further studies. Developed set of plugins are packaged with the name of \textit{CrossOrgProcMin}\footnote{\url{http://www.promtools.org/prom6/packages/CrossOrgProcMin}} and published open-source\footnote{\url{http://github.com/onuryilmaz/cross-org-proc-min}} being available in the latest version of ProM release.

### 2015-09-08 5_results_discussions/coselog-wabo/coselog-wabo.tex
no message

\subsection{Environmental Permit Application Process}
\label{subsec:coselog-wabo-process}

>>>>

\subsection{Environmental Permit Application Process}
\label{subsec:coselog-wabo-process}
\textit{Environmental Permit Application Process} dataset originates from the "Configurable Services for Local Governments (CoSeLoG)" project \cite{van2011business} which investigates the similarities and dissimilarities between several processes of different municipalities in Netherlands. Dataset contains records of receiving phase for the building permit application process in 5 municipalities, which are comparable since activity labels in the different event logs refer to the same activities performed in five municipalities. In this dataset \cite{coselog-data}, there are total of 1214 cases and 2142 events with a variable distribution between event logs of municipalities and municipalities are used as organizational logs.

\begin{itemize}
  \item In \textit{Process Model Mining} stage, with 10\% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#4 and \#5 resulted with low appropriateness values. 
  \item In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered and three clusters are created: Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases on most of the cases. When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process model compared to others, fails in spotting mismatch patterns according to \textit{graph-edit similarity}.
  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points. For instance, cluster of Municipality \#1 performs worse in 6 indicators with the difference of 25 \% and on average 5 mismatch patterns are listed for each performance indicator. When it is compared to the total mismatch patterns of Municipality #1, which is 357, proposed approach helps significantly to the user for focusing performance improvement.
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{5_results_discussions/coselog-wabo/recommendation-generation-analysis-k3}
		\caption{Recommendation Generation analysis for Environmental Permit Application Process dataset (3 Clusters)}
	  \label{fig:coselog-wabo-recommendation-generation-analysis-k3}
	\end{figure}
\end{itemize}

### 2015-09-08 5_results_discussions/loan-application-process/loan-application-process.tex
no message

\subsection{Loan Application Process}
\label{subsec:loan-app-process}

In \textit{Loan Application Process} dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this thesis study is be applied.

\begin{itemize}
  \item In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.
  \item In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators. In order to avoid overfitting,  with two clusters, Variant \#1, \#2, and \#4 are grouped into one cluster where only Variant \#3 is left to other cluster. 
  \item In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization. As the similarity between process models decreases our method spots more mismatch patterns for most of the variants and it ensures that the developed mismatch pattern analyzers work as expected for this dataset. 
  \item In \textit{Recommendation Generation} stage, an organization and performance difference threshold is selected as analysis input. For the selected organization's cluster, all other clusters are checked for performing better than the specified threshold. Instead of all mismatch patterns between organizations, only the mismatch patterns that are potential causes of other organizations to perform better are listed. For different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}. 
    \begin{figure}
    	\centering
    	\includegraphics[width=\textwidth]{5_results_discussions/loan-application-process/recommendation-generation-analysis}
    	\caption{Recommendation Generation analysis for Loan Application Process dataset}
      \label{fig:loan-recommendation-generation-analysis}
    \end{figure}
  In order to construct the data in Figure~\ref{fig:loan-recommendation-generation-analysis}, every organization is selected one-by-one with different threshold values. For every analysis, number of performance indicators and average number of mismatch patterns causing them are plotted. In addition, total number of mismatch patterns without clustering for each organization is added to the plot as an upper bound. With the help of this upper bound, responsiveness and degree of helping the user to focus on the performance improvement can be analyzed. As can be seen, for each threshold value, average number of mismatch patterns \textit{with performance indicator clustering} are very low compared to \textit{without clustering}. In other words, when user wants to improve its performance with any threshold, there is significantly less number of mismatch patterns on average to check. This shows the methodology proposed in this thesis can help users to focus on differences between organizations given this dataset.
\end{itemize}

>>>>

\subsection{Loan Application Process}
\label{subsec:loan-app-process}
\textit{Loan Application Process} dataset is synthetically created and consists of four variants of a simple loan application in a financial institute. These event logs are used to test different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}. In this dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this thesis study is be applied.

\begin{itemize}
  \item In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.
  \item In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators. In order to avoid overfitting,  with two clusters, Variant \#1, \#2, and \#4 are grouped into one cluster where only Variant \#3 is left to other cluster. 
  \item In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization. As the similarity between process models decreases our method spots more mismatch patterns and it ensures that the developed mismatch pattern analyzers work as expected for this dataset. 
  \item In \textit{Recommendation Generation} stage, for different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}. 
    \begin{figure}
    	\centering
    	\includegraphics[width=\textwidth]{5_results_discussions/loan-application-process/recommendation-generation-analysis}
    	\caption{Recommendation Generation analysis for Loan Application Process dataset}
      \label{fig:loan-recommendation-generation-analysis}
    \end{figure}
  In order to construct the data in Figure~\ref{fig:loan-recommendation-generation-analysis}, every organization is selected one-by-one with different threshold values. For each analysis, number of performance indicators and average number of mismatch patterns causing them are plotted. In addition, total number of mismatch patterns without clustering is added as an upper bound. With the help of this upper bound, responsiveness and degree of helping the user to focus on the performance improvement can be analyzed. As can be seen, for each threshold value, average number of mismatch patterns \textit{with performance indicator clustering} are very low compared to \textit{without clustering}. In other words, when user wants to improve its performance with any threshold, there is significantly less number of mismatch patterns on average to check. This shows the methodology proposed in this study can help users to focus on differences between organizations given this dataset.
\end{itemize}
